03 - PubliliaFitness - Modeling offspring surivorship

### 2023-08-26 scripts/Publilia-03-survivorship.Rmd
Moved Zink fitness analysis to it's own script + saved survorship model fits from script 03 to use in 05 + other minor edits to script 05 to run without error

models_output <- list(
  hatch = des_hatch.desL.ant_treatment.quad$fits,
  Nsurv = des_Nsurv.desL.ant_treatment.quad$fits,
  Esurv = des_Esurv.desL.ant_treatment.quad$fits
)
```

@@

### Print model outputs
#### Hatch
```{r}
print_glm_stats(models_output$hatch)
```

#### Nsurv
```{r}
print_glm_stats(models_output$Nsurv)
```

#### Esurv
```{r}
print_glm_stats(models_output$Esurv)
```

@@

>>>>

surv_model_fits <- list(
  hatch = des_hatch.desL.ant_treatment.quad$fits,
  Nsurv = des_Nsurv.desL.ant_treatment.quad$fits,
  Esurv = des_Esurv.desL.ant_treatment.quad$fits
)
```

@@

### Print model outputs
#### Hatch
```{r}
print_glm_stats(surv_model_fits$hatch)
```

#### Nsurv
```{r}
print_glm_stats(surv_model_fits$Nsurv)
```

#### Esurv
```{r}
print_glm_stats(surv_model_fits$Esurv)
```

@@

## Save Main model fits for estimating fitness

```{r}
write_rds(surv_model_fits, here("saved_rds/surv_model_fits.rds"))
```
